Embedding Dimension of Polyhedral Losses

### 2020-01-31 colt-20/embed-dim.tex
Tweaking appendix proofs of polytope things

\section{$d$-dimensional omitted proofs}\label{app:omitted-d-dim}
\begin{proof}[Proof of Lemma~\ref{lemma:minkowski-support}]
	\jessie{Appendix}
	For each $p$, $\oplus_p \T$ is a polytope.
	\bo{TODO: it turns out that $p$ doesn't matter, only its support; and there are only finitely many possible supports (or even better, the normals that are complete for the uniform minkowski sum turn out to be complete for all other $p$-combinations).}
	For each of the finitely many supports ($2^n - 1$), we know $\oplus_p \T$ is a polytope, and every polytope can be defined by a finite, complete set of vectors for that polytope.
	As a two polytopes with the same support are combinatorially equivalent\jessiet{is this what we want?  I know the idea but not sure if this is the proper term}, they can be defined by the same facet enumeration, and any set of normals that is complete for $\oplus_p \T$ is also complete for a $\oplus_{p'}\T$ if $\supp(p) = \supp(p')$.
	We can simply concatenate these finite set of normals for the finite polytope supports, with some normals possibly becoming redundant.
	This yields finitely many normals defining the weighted Minkowski sum $\oplus_p \T$ for all $p \in \simplex$.
\end{proof}

\begin{proof}[Proof of Lemma~\ref{lemma:D-polytope}]
	\jessie{Appendix}
	Recall by definition, the notation $\oplus_p \T = \{\sum_y p_y x_y : x_y \in T_y (\forall y)\}$.
	Each $T_y$ is a polytope, so $p_y T_y$ is a polytope.
	The Minkowski sum of polytopes is a polytope, so $\oplus_p \T$ is a polytope by~\cite[Section 1.2]{weibel2007minkowski}.
	\bo{TODO}\jessie{Taking a try}
	Since $\oplus_p \T$ is a polytope for all $p \in \simplex$, we know there is a halfspace representation of normals $V$ so that for all $y \in \Y$, we have $x \in p_yT_y \iff \inprod{V}{x} \leq p_y e^y$ for some matrix $V$ and the support vector $e^y$, where $e^y_i = H_{T_y}(V_i)$.
	By Lemma~\ref{lemma:minkowski-support}, we know that there is a set of normals $V^*$ that is complete for $T(p)$ for all $p \in \simplex$.
	We construct $E^*$ as the support matrix for this complete set of normals.
    We know that the support of the Minkowski sum for a given normal is the sum of the normals~\cite[Theorem 3.1.6]{weibel2007minkowski}, and so we we can take the $x \in \oplus_p \T \iff \inprod{V^*}{x} \leq E^*p$.
	Substituting $x = \vec 0$, we see $\vec 0 \in \oplus_p \T \iff Ep \geq \vec 0 \iff p \in D(\T)$ by Lemma~\ref{lem:describe-D}, which defines a polytope by construction of $E$.
\end{proof}

>>>>

\section{$d$-dimensional omitted proofs}\label{app:omitted-d-dim}
\begin{proof}[Proof of Lemma~\ref{lemma:minkowski-support}]
	For each $p$, $\oplus_p \T$ is a polytope.
	\bo{TODO: it turns out that $p$ doesn't matter, only its support; and there are only finitely many possible supports (or even better, the normals that are complete for the uniform minkowski sum turn out to be complete for all other $p$-combinations).}
	For each of the finitely many supports ($2^n - 1$), we know $\oplus_p \T$ is a polytope, and every polytope can be defined by a finite, complete set of vectors for that polytope.
	As a two polytopes with the same support are combinatorially equivalent\jessiet{is this what we want?  I know the idea but not sure if this is the proper term}, they can be defined by the same facet enumeration, and any set of normals that is complete for $\oplus_p \T$ is also complete for a $\oplus_{p'}\T$ if $\supp(p) = \supp(p')$.
	We can simply concatenate these finite set of normals for the finite polytope supports, with some normals possibly becoming redundant.
	This yields finitely many normals defining the weighted Minkowski sum $\oplus_p \T$ for all $p \in \simplex$.
\end{proof}

\begin{proof}[Proof of Lemma~\ref{lemma:D-polytope}]
	Recall by definition, the notation $\oplus_p \T = \{\sum_y p_y x_y : x_y \in T_y (\forall y)\}$.
	Each $T_y$ is a polytope, so $p_y T_y$ is a polytope.
	The Minkowski sum of polytopes is a polytope, so $\oplus_p \T$ is a polytope by~\cite[Section 1.2]{weibel2007minkowski}.
	\bo{TODO}\jessie{Taking a try}
	Since $\oplus_p \T$ is a polytope for all $p \in \simplex$, we know there is a halfspace representation of normals $V$ so that for all $y \in \Y$, we have $x \in p_yT_y \iff \inprod{V}{x} \leq p_y e^y$ for some matrix $V$ and the support vector $e^y$, where $e^y_i = H_{T_y}(V_i)$.
	By Lemma~\ref{lemma:minkowski-support}, we know that there is a set of normals $V^*$ that is complete for $T(p)$ for all $p \in \simplex$.
	We construct $E^*$ as the support matrix for this complete set of normals.
    The support of the Minkowski sum for a given normal is the sum of the normals~\cite[Theorem 3.1.6]{weibel2007minkowski}, and so we we can take the $x \in \oplus_p \T \iff \inprod{V^*}{x} \leq E^*p$.
	Substituting $x = \vec 0$, we see $\vec 0 \in \oplus_p \T \iff E^*p \geq \vec 0 \iff p \in D(\T)$ by Lemma~\ref{lem:describe-D}, which defines a polytope by construction of $E^*$.
\end{proof}
